---
title: 'Feedback for 12345'
format: 
 html: 
  self-contained: true
  toc: true
css: "../../www/css.css"    
knitr: 
  opts_chunk: 
    eval: false
---

```{r eval=TRUE, echo= FALSE}
here::here('shiny_markR/www/helpers.R') |> source()
```

```{r eval=TRUE, echo= FALSE, message=FALSE}
grade_csv <- here::here('shiny_markR/student_feedback_files/csv/12345.csv') |> readr::read_csv()
```

## Marking rubric 

```{r eval=TRUE, echo= FALSE}
generate_rubric(grid = grid, grade_csv$points_analysis, grade_csv$points_theory, grade_csv$points_coding, grade_csv$points_org)
```

## Feedback

### Analysis 

This is an example of a comment. 

This is another comment. Each comment should start on a new line and be separated by an additional blank line. 

Section headings should be denoted by two asterisks on each end (as if making the headings bold). 

Comments can also use markdown formatting. You can use italics (_) or bold text (double *) to emphasise points, or use backticks for code formatting. Formatting will not show within the app, but they will be visible in the rendered document. 

You can also use bullet points If you're using bullet points, they need to be on the same line, separated by a vertical line. For example: 

 - This is a first bullet point 

 - This is a second bullet point 

 - This is a third bullet point. 



### Theoretical understanding 

LaTeX math works in the comments as you would expect. For example, this:  $\hat{\beta}$ will render as a nice beta hat symbol. 

Similarly, you can render whole equations with a combination of vertical lines and double dollar signs, such as: 

$$ Y_i = \beta_0 + \beta_1 X_{1i} + \varepsilon_i $$





### Coding 

You can prepare some comments that showcase code. 

Here's an example of such a comment, using a vertical line to indicate a new line: 

```{r} 

 add some example code here 

```

Codechunks in the feedback are not evaluated - this is set in the `shiny_markR/feedback_yaml` file. 

### Organization 

Here's a comment about organisation. 

Here's another comment about organisation. You can make these comments as long or as brief as needed. 



### Overall 

Add an overall comment, summarising things to focus on. 

Things you've done well: 

 - Thing 1 

 - Thing 2 

 - Thing 3 

 Things to work on for future assignments: 

 - Thing 1 

 - Thing 2 

 - Thing 3 



```{r eval=TRUE, echo= FALSE, child='../../rubric_files/rubric_text.qmd'}

```
